---
title: 'Developing Data Products Course Project 3: Shiny Application and Reproducible
  Pitch'
author: "Eric Lu"
date: "4/4/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment 

The Shiny App requires:  
1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.  
2. Deploy the application on Rstudio's shiny server  
3. Share the application link by pasting it into the provided text box  
4. Share your server.R and ui.R code on github  

The presentation requires:  
1. 5 slides to pitch our idea done in Slidify or Rstudio Presenter  
2. Your presentation pushed to github or Rpubs  
3. A link to your github or Rpubs presentation pasted into the provided text box  

## My Shiny App

It can be found here:   
https://zlu00.shinyapps.io/developing_data_products_course_project_3/

This app is about my mock trading stock portfolio.  
In this app, you can:  
1. Select one or multiple stock symbols.  
2. Select a chart type.  
3. Select a date range.  

Once you hit the submit button, the server will utilize the quantmod library, which collects and displays stock price for each stock symbols. 

## Sample plot 1
Here is a sample plot of AAPL stock price in a candlesticks chart.
```{r, message=FALSE, warning=FALSE}
library(quantmod)
getSymbols("AAPL")
chartSeries(AAPL, type = "candlesticks", subset = '2017-03-04::2017-04-04', theme = chartTheme("black", up.col="green", dn.col="red"), TA = NULL)
```

## Sample plot 2
Here is a sample plot of BABA stock price in a line chart.
```{r, message=FALSE, warning=FALSE}
getSymbols("BABA")
chartSeries(BABA, type = "line", subset = '2017-03-04::2017-04-04', theme = chartTheme("black", up.col="green", dn.col="red"), TA = NULL)
```

